### 2023-12-15 main.tex
ll

 As already pointed out the dual process eventually voids the chain by piling up particles of species $\{1,\ldots,N-1\}$ in the extra sites $0$ and $L+1$ and replacing them by the holes $N$. This property allows to characterize the steady state non-equilibrium distribution (that is unique) by the probability that dual particles are absorbed in the extra-sites, called \textit{absorption probabilities}. This is a generalization for the non-integrable chain of the Corollary~\ref{Corolollary-ABS_Corr-abstract}. The process $\left(\bm{n}(t)\right)_{t\geq0}$ has generator

@@

The process is dual to $(\bm{\xi}(t))_{t\geq0}$, defined on the dual state space $\widetilde{\Omega}_{L}$, has generator

@@

where $\mathcal{L}_{x,x+1}$ is given by \eqref{Generator} and where the boundary generators $\widetilde{\mathcal{L}}_{\text{left}}$ and $\widetilde{\mathcal{L}}_{\text{right}}$ are given in \eqref{siteDualGenerator}: they absorb particles from sites $1$ and $L$ and put them at extra-sites $0$ and $L+1$ respectively. The duality function reads is \eqref{dualityElements} specified on the chain. 

@@

Therefore, up to this constant, $\mathbb{E}_{\mu_{\text{NESS}}}\left[D(\bm{n},\bm{\xi})\right]$ gives the $m-$points correlations at non-equilibrium steady state. The following equalities hold using ergodicity and duality:

@@

 These correlations can be computed once the absorption probabilities are known. For example, we report in Appendix~\ref{appendix-1pts-general} the solution for the simplest case of one point correlations that is exactly solvable, since the single dual particle behaves as an independent random walker. The absorption probabilities for higher point correlations fulfill  difference equations.

@@

\appendix 
\section*{Appendix}
\section{Interpretation of $\Psi^{'}$ as marginals of the steady state distribution}\label{subsection-interpretationPSIp} 
We still miss the interpretation of $\Psi^{'}(\bm{\tau})$ when  $\bm{\tau}= (N,\ldots,N)$. We show here that for this particular configuration
$\Psi^{'}(N,\ldots,N) =1$. Indeed, for any $\bm{\tau}\in \Omega^{'}$ we have that 
\begin{align}
	\Psi^{'}(\bm{\tau})=&\langle\bm{\tau}|\Psi^{'}\rangle=\sum_{\bm{\sigma}\in \Omega^{'}}\langle \bm{\tau}|S_{1}|\bm{\sigma}\rangle\langle \bm{\sigma}|\Psi\rangle=\sum_{\bm{\sigma}\in \Omega^{'}}\langle \bm{\sigma}|S_{1}^{T}|\bm{\tau}\rangle\langle \bm{\sigma}|\Psi\rangle\dt
\end{align} 
We introduce the dual configuration $\bm{\xi}(\bm{\tau})=(N,\tau_{1},\ldots,\tau_{L},N)$ where two extra-sites occupied by the species $N$ have been attached to the vector $\bm{\tau}$, transforming it from a vector of dimension $L$ to one of dimension $L+2$. More explicitly, this dual configuration is given by
\begin{equation}
	\begin{cases}
		\xi_{a}^{x}(\bm{\tau})= \delta_{\tau_{x},a}\qquad \forall a\in \{1,\ldots N\}\quad \forall x\in \{1,\ldots,L\}\\
		\xi_{N}^{0}(\bm{\tau})=\xi_{N}^{L+1}(\bm{\tau})=1
	\end{cases}\dt
\end{equation} Now we consider the elements $\langle\bm{\sigma}|D|\xi(\bm{\tau})\rangle$ of the duality matrix $D$ and we have
\begin{align}\label{useful-InInterpretation}
	\Psi^{'}(\bm{\tau})=&\sum_{\bm{\sigma}\in \Omega^{'}}\langle \bm{\sigma}|D|\bm{\xi}(\bm{\tau})\rangle\langle \bm{\sigma}|\Psi\rangle\dt
\end{align}
We observe that for any $x\in \{1,\ldots,L\}$
\begin{equation}
	\prod_{a=1}^{N-1}\mathbbm{1}_{\{\delta_{\sigma_{x},a}\geq\xi_{a}^{x}(\bm{\tau})\}}=\left(\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)^{(1-\delta_{\tau_{x},N})}%=\begin{cases}
		%	\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\qquad &\text{if}\quad \tau_{x}\neq N\\
		%	1\qquad  &\text{if}\quad \tau_{x}= N
		%	\end{cases}\dt
\end{equation}
Indeed, we have that 
\begin{equation}
	\prod_{a=1}^{N-1}\mathbbm{1}_{\{\delta_{\sigma_{x},a}\geq\xi_{a}^{x}(\bm{\tau})\}}=\begin{cases}
		\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\qquad &\text{if}\quad \tau_{x}\neq N\\
		1\qquad  &\text{if}\quad \tau_{x}= N
	\end{cases}\dt
\end{equation}
Therefore using the duality function \eqref{ElementsDualityMatrixChain_1} and equation~\ref{useful-InInterpretation}, we obtain 
\begin{equation}%\label{interpretation-PsiP}
	\Psi^{'}(\bm{\tau})=\mathbb{E}\left[\prod_{x=1}^{L}\left(\mathbbm{1}_{\{Y_{x}=\tau_{x}\}} \right)^{(1-\delta_{\tau_{x},N})}\right]\dt
\end{equation} 
This last equation completes and generalizes \eqref{corr-psi1} by showing that $\Psi^{'}(N,\ldots,N) =1$.

@@

	\left(\mathcal{L}_{\text{left}}^{TH}D(\cdot,\bm{\xi})\right)(\bm{n})&=\left(\widetilde{\mathcal{L}}_{\text{left}}^{TH}D(\bm{n},\cdot)\right)(\bm{\xi})\label{boundaryDualityTH}

@@

	d(n^{x},\xi^{x}):=\frac{(\nu-\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}

@@

	\frac{\nu!}{r_{1}!\cdots r_{N}!}\left(\prod_{a=1}^{N-1}\left(\frac{\alpha_{a}}{\alpha_{N}}\right)^{r_{a}}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu}\right)
We consider the first addend in the curly bracket of the \eqref{ProvaBordoTH}. We add and remove $\xi_{a}^{1}$ at the exponent of $\left(\frac{\alpha_{a}}{|\alpha|}\right)$ and then we multiplying this first addend by $\left(\frac{\alpha_{N}}{|\alpha|}\right)^{-(r_{1}^{1}+\ldots+r_{N-1})+(r_{1}^{1}+\ldots+r_{N-1})}$. Thus, we have

@@

	\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{\text{left}}\right)^{\xi_{a}^{0}+\xi_{a}^{1}}\right)\left(\prod_{x=2}^{L}d(n^{x},\xi^{x})\right)\left(\prod_{d=1}^{N-1}(\rho_{d}^{\text{right}})^{\xi_{d}^{L+1}}\right)

@@

@@

	\left(\widetilde{\mathcal{L}}_{\text{left}}^{TH}D(\bm{n},\cdot)\right)(\bm{\xi})

@@

		\mathcal{L}_{x,x+1}^{rd}n_{d}^{x}&=\nu \sigma_{11}(n_{d}^{x+1}-n_{d}^{x})+\nu\sigma_{12}\sum_{b=1\,:	,b\neq d}^{N-1}(n_{b}^{x+1}-n_{d}^{x})+(\Upsilon-2\nu\sigma_{12})\sum_{b=1}^{N-1}(n_{b}^{x}-n_{\alpha}^{x})

@@

	\mathcal{L}_{x,x+1}n_{d}^{x}=\sum_{A,B=1}^{N}n_{A}^{x}n_{B}^{x+1}\left((n_{d}^{x}-\bm{\delta}_{A}^{x}+\bm{\delta}_{B}^{x}+\bm{\delta}_{A}^{x+1}-\bm{\delta}_{B}^{x+1})-n_{d}^{x}\right)

@@

		\mathcal{L}_{x,x+1}^{c}n_{d}^{x}&=\sum_{A,B=1}^{N}n_{A}^{x}n_{B}^{x+1}\left((n_{d}^{x}-\bm{\delta}_{A}^{x}+\bm{\delta}_{h_{c}(B)}^{x}+\bm{\delta}_{h_{c}(A)}^{x+1}-\bm{\delta}_{B}^{x+1})-n_{d}^{x}\right)

>>>>

 As already pointed out, the dual process voids the chain by piling up particles of species $\{1,\ldots,N-1\}$ in the extra sites $0$ and $L+1$ and replacing them by the holes $N$. This property allows to characterize the steady state non-equilibrium distribution (that is unique) by the probability that dual particles are absorbed in the extra-sites, called \textit{absorption probabilities}. This is a generalization for the non-integrable chain of the Corollary~\ref{Corolollary-ABS_Corr-abstract}. The process $\left(\bm{n}(t)\right)_{t\geq0}$ has generator

@@

The process is dual to $(\bm{\xi}(t))_{t\geq0}$, defined on the dual state space $\widetilde{\Omega}_{L}$, and has generator

@@

where $\mathcal{L}_{x,x+1}$ is given by \eqref{Generator} and where the boundary generators $\widetilde{\mathcal{L}}_{\text{left}}$ and $\widetilde{\mathcal{L}}_{\text{right}}$ are given in \eqref{siteDualGenerator}: they absorb particles from sites $1$ and $L$ and put them at extra-sites $0$ and $L+1$ respectively. The duality function is \eqref{dualityElements} specified on the chain. 

@@

Therefore, up to this constant, $\mathbb{E}_{\mu_{\text{NESS}}}\left[D(\bm{n},\bm{\xi})\right]$ gives the $m-$point correlations in the non-equilibrium steady state. The following equalities hold using ergodicity and duality:

@@

 These correlations can be computed once the absorption probabilities are known. For example, we report in Appendix~\ref{appendix-1pts-general} the solution for the simplest case of one-point correlations that is exactly solvable, since the single dual particle behaves as an independent random walker. The absorption probabilities for higher point correlations fulfill  difference equations.

@@

\appendix 
\section*{Appendix}
\section{Interpretation of $\Psi^{'}$ as marginals of the steady state distribution}\label{subsection-interpretationPSIp} 
We still miss the interpretation of $\Psi^{'}(\bm{\tau})$ when  $\bm{\tau}= (N,\ldots,N)$. We show here that for this particular configuration
$\Psi^{'}(N,\ldots,N) =1$. Indeed, for any $\bm{\tau}\in \Omega^{'}$ we have that 
\begin{align}
	\Psi^{'}(\bm{\tau})=&\langle\bm{\tau}|\Psi^{'}\rangle=\sum_{\bm{\sigma}\in \Omega^{'}}\langle \bm{\tau}|S_{1}|\bm{\sigma}\rangle\langle \bm{\sigma}|\Psi\rangle=\sum_{\bm{\sigma}\in \Omega^{'}}\langle \bm{\sigma}|S_{1}^{T}|\bm{\tau}\rangle\langle \bm{\sigma}|\Psi\rangle\dt
\end{align} 
We introduce the dual configuration $\bm{\xi}(\bm{\tau})=(N,\tau_{1},\ldots,\tau_{L},N)$ where two extra-sites occupied by the species $N$ have been attached to the vector $\bm{\tau}$, transforming it from a vector of dimension $L$ to one of dimension $L+2$. More explicitly, this dual configuration is given by
\begin{equation}
	\begin{cases}
		\xi_{a}^{x}(\bm{\tau})= \delta_{\tau_{x},a}\qquad \forall a\in \{1,\ldots N\}\quad \forall x\in \{1,\ldots,L\}\\
		\xi_{N}^{0}(\bm{\tau})=\xi_{N}^{L+1}(\bm{\tau})=1
	\end{cases}\dt
\end{equation} Now we consider the elements $\langle\bm{\sigma}|D|\xi(\bm{\tau})\rangle$ of the duality matrix $D$ and we have
\begin{align}\label{useful-InInterpretation}
	\Psi^{'}(\bm{\tau})=&\sum_{\bm{\sigma}\in \Omega^{'}}\langle \bm{\sigma}|D|\bm{\xi}(\bm{\tau})\rangle\langle \bm{\sigma}|\Psi\rangle\dt
\end{align}
We observe that for any $x\in \{1,\ldots,L\}$
\begin{equation}
	\prod_{a=1}^{N-1}\mathbbm{1}_{\{\delta_{\sigma_{x},a}\geq\xi_{a}^{x}(\bm{\tau})\}}=\left(\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\right)^{(1-\delta_{\tau_{x},N})}%=\begin{cases}
		%	\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\qquad &\text{if}\quad \tau_{x}\neq N\\
		%	1\qquad  &\text{if}\quad \tau_{x}= N
		%	\end{cases}
		\dt
\end{equation}
Indeed, we have that 
\begin{equation}
	\prod_{a=1}^{N-1}\mathbbm{1}_{\{\delta_{\sigma_{x},a}\geq\xi_{a}^{x}(\bm{\tau})\}}=\begin{cases}
		\mathbbm{1}_{\{\sigma_{x}=\tau_{x}\}}\qquad &\text{if}\quad \tau_{x}\neq N\\
		1\qquad  &\text{if}\quad \tau_{x}= N
	\end{cases}\dt
\end{equation}
Therefore using the duality function \eqref{ElementsDualityMatrixChain_1} and equation~\ref{useful-InInterpretation}, we obtain 
\begin{equation}%\label{interpretation-PsiP}
	\Psi^{'}(\bm{\tau})=\mathbb{E}\left[\prod_{x=1}^{L}\left(\mathbbm{1}_{\{Y_{x}=\tau_{x}\}} \right)^{(1-\delta_{\tau_{x},N})}\right]\dt
\end{equation} 
This last equation completes and generalizes \eqref{corr-psi1} by showing that $\Psi^{'}(N,\ldots,N) =1$.

@@

	\left(\mathcal{L}_{\text{left}}^{TH}D(\cdot,\bm{\xi})\right)(\bm{n})&=\left(\widetilde{\mathcal{L}}_{\text{left}}^{TH}D(\bm{n},\cdot)\right)(\bm{\xi})\dt\label{boundaryDualityTH}

@@

	d(n^{x},\xi^{x}):=\frac{(\nu-\sum_{a=1}^{N-1}\xi_{a}^{x})!}{\nu!}\prod_{a=1}^{N-1}\frac{n_{a}^{x}!}{(n_{a}^{x}-\xi_{a}^{x})!}\dt

@@

	\frac{\nu!}{r_{1}!\cdots r_{N}!}\left(\prod_{a=1}^{N-1}\left(\frac{\alpha_{a}}{\alpha_{N}}\right)^{r_{a}}\left(\frac{\alpha_{N}}{|\alpha|}\right)^{\nu}\right)\dt
We consider the first addend in the curly bracket of the \eqref{ProvaBordoTH}. We add and remove $\xi_{a}^{1}$ at the exponent of $\left(\frac{\alpha_{a}}{|\alpha|}\right)$ and then we multiplying this first addend by $\left(\frac{\alpha_{N}}{|\alpha|}\right)^{-(r_{1}^{1}+\ldots+r_{N-1})+(r_{1}^{1}+\ldots+r_{N-1})}$.\todo{fix text?} Thus, we have

@@

	\left(\prod_{a=1}^{N-1}\left(\rho_{a}^{\text{left}}\right)^{\xi_{a}^{0}+\xi_{a}^{1}}\right)\left(\prod_{x=2}^{L}d(n^{x},\xi^{x})\right)\left(\prod_{d=1}^{N-1}(\rho_{d}^{\text{right}})^{\xi_{d}^{L+1}}\right)\dt

@@

\todo{doublecheck}

@@

	\left(\widetilde{\mathcal{L}}_{\text{left}}^{TH}D(\bm{n},\cdot)\right)(\bm{\xi})\dt

@@

		\mathcal{L}_{x,x+1}^{rd}n_{d}^{x}&=\nu \sigma_{11}(n_{d}^{x+1}-n_{d}^{x})+\nu\sigma_{12}\sum_{b=1\,:	,b\neq d}^{N-1}(n_{b}^{x+1}-n_{d}^{x})+(\Upsilon-2\nu\sigma_{12})\sum_{b=1}^{N-1}(n_{b}^{x}-n_{\alpha}^{x})\dt

@@

	\mathcal{L}_{x,x+1}n_{d}^{x}=\sum_{A,B=1}^{N}n_{A}^{x}n_{B}^{x+1}\left((n_{d}^{x}-\bm{\delta}_{A}^{x}+\bm{\delta}_{B}^{x}+\bm{\delta}_{A}^{x+1}-\bm{\delta}_{B}^{x+1})-n_{d}^{x}\right)\dt

@@

		\mathcal{L}_{x,x+1}^{c}n_{d}^{x}&=\sum_{A,B=1}^{N}n_{A}^{x}n_{B}^{x+1}\left((n_{d}^{x}-\bm{\delta}_{A}^{x}+\bm{\delta}_{h_{c}(B)}^{x}+\bm{\delta}_{h_{c}(A)}^{x+1}-\bm{\delta}_{B}^{x+1})-n_{d}^{x}\right)\dt
